data exploration

### 2021-04-09 outputs/exploratory.Rmd
add models

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
```

```{r}
isrdata <- read.dta13("inputs/data/Instructor-Student Relationships Experiment Data_Anonymous.dta")
```

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(readstata13)
library(arsenal)
library(Hmisc)
library(MASS)
library(kableExtra)
library(apaTables)
```

```{r}
codebook <- read_csv(here("inputs/data/codebook.csv"))
```

```{r, warning=FALSE}
isrdata <- read.dta13(here("inputs/data/Instructor-Student Relationships Experiment Data_Anonymous.dta"))
```

@@

```{r}
summary(tableby(treatment ~  s1_sim + s1_tsr + s2_sim + s2_tsr + t2_sim1 + t2_tsr + grade + std_grade + t2_finalexam + f17_enrolled + ir_f16_gpa + s_female,
                data = isrdata)) %>%
  kable()
```

```{r}
rcorr(as.matrix(isrdata %>% 
                  dplyr::select(s1_sim, s1_tsr, s2_sim, s2_tsr, t2_sim1, t2_tsr, grade, std_grade, t2_finalexam, ir_f16_gpa)))
```

```{r}
apa.cor.table(isrdata %>% 
                  dplyr::select(s1_sim, s1_tsr, s2_sim, s2_tsr, t2_sim1, t2_tsr, grade, std_grade, t2_finalexam, ir_f16_gpa))
```

@@

```{r}
summary(lm(data = isrdata, s1_sim ~ treatment))
```
```{r}
summary(lm(data = isrdata, s2_sim ~ treatment))
```
```{r}
summary(lm(data = isrdata, s2_tsr ~ treatment + s1_tsr))
```
```{r}
summary(polr(formula = as.factor(t2_sim1) ~ treatment, data = isrdata, Hess = TRUE))
```

```{r}
summary(lm(data = isrdata, s2_tsr ~ treatment))
```

```{r}
summary(lm(data = isrdata, grade ~ treatment + s1_female + ir_f16_gpa))
```

```{r}
summary(lm(data = isrdata %>% filter(obj_exam == 1), t2_finalexam ~ treatment + s1_female + ir_f16_gpa))
```

```{r}
summary(glm(data = isrdata, f17_enrolled ~ treatment + s1_female + ir_f16_gpa, family = "binomial"))
```
